Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
marking with TBD.
Comment paragraph about "behavior is imperative"

\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}
\authorinfo{Simon HENGEL}
           {}
           {sol@typeful.net}
\authorinfo{Markus KLINIK}
           {Elektrobit Automotive GmbH}
           {markus.klinik@elektrobit.com}

@@

@@

\noindent The word ``behavior'' might be associated with ``imperative
action''.  Since pure functions of Haskell are static, this word might
be improper for Haskell.  However, this word is already used in the
Haskell community~\cite{typeclassopedia}.  So, we use ``behavior''
instead of defining terminology in this paper.

@@

\begin{quote}
\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.

@@

\begin{quote}
    \begin{itemize}
        \item Add "best current practice"
        \item We showed how to reuse pieces of specifications
    \end{itemize}
\end{quote}

>>>>

\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}
\authorinfo{Simon HENGEL}
           {TBD}
           {sol@typeful.net}
\authorinfo{Markus KLINIK}
           {Elektrobit Automotive GmbH}
           {markus.klinik@elektrobit.com}

@@

TBD:

@@

%\noindent The word ``behavior'' might be associated with ``imperative
%action''.  Since pure functions of Haskell are static, this word might
%be improper for Haskell.  However, this word is already used in the
%Haskell community~\cite{typeclassopedia}.  So, we use ``behavior''
%instead of defining terminology in this paper.

@@

\begin{quote}
TBD:
\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.

@@

\begin{quote}
TBD:
    \begin{itemize}
        \item Add "best current practice"
        \item We showed how to reuse pieces of specifications
    \end{itemize}
\end{quote}
